Our Galactocentric Reference Frame Is Probably Wrong, and Not by a Little

### 2018-12-04 paper/ms.tex
Fix previous commit
Update paper

\newcommand{\Msun}{\text{M}_\odot}
\newcommand{\pc}{\text{pc}}
\newcommand{\kpc}{\text{kpc}}
\newcommand{\Myr}{\text{Myr}}
\newcommand{\Gyr}{\text{Gyr}}
\newcommand{\kms}{\text{km}/\text{s}}

@@

@@

\author{Angus Beane}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 5th
Ave., New York, NY 10010, USA}
\affil{Department of Physics \& Astronomy, University of Pennsylvania, 209
South 33rd St., Philadelphia, PA 19104, USA}

\author{Many Helpful People}
\noaffiliation

@@

\begin{figure*}
\plotone{cartoon.pdf}
\caption{Caption.}
\label{fig:cartoon}
\end{figure*}

@@

@@

To compute the forces from the frozen potential, we use the simple tree code
\texttt{pykdgrav}\footnote{\url{https://github.com/omgspace/pykdgrav},
commit:\texttt{fbd1ddc}}.

We use the initial position and velocity of two star particles in
$\texttt{m12i}$

>>>>

\newcommand{\Msun}{\text{M}_\odot}
\newcommand{\pc}{\text{pc}}
\newcommand{\kpc}{\text{kpc}}
\newcommand{\Myr}{\text{Myr}}
\newcommand{\Gyr}{\text{Gyr}}
\newcommand{\kms}{\text{km}/\text{s}}
\newcommand{\actunit}{\text{kpc}\,\kms}

@@

% affiliations
\newcommand{\cca}{Center for Computational Astrophysics, Flatiron Institute, 162 5th
Ave., New York, NY 10010, USA}
\newcommand{\penn}{Department of Physics \& Astronomy, University of Pennsylvania, 209
South 33rd St., Philadelphia, PA 19104, USA}
\newcommand{\amnh}{Department of Astrophysics, American Museum of Natural History, Central Park West at 79th St., New York, NY 10024, USA}
\newcommand{\columbia}{Department of Astronomy, Columbia University, 550 W 120th St., New York, NY 10027, USA}

@@

\author{Angus Beane}
\affil{\cca}
\affil{\penn}

\author{Robyn Sanderson}
\affil{\cca}
\affil{\penn}

\author{Mordecai-Mark Mac Low}
\affil{\cca}
\affil{\amnh}

\author{Melissa K. Ness}
\affil{\cca}
\affil{\columbia}

\author{Daniel Angl\'es-Alc\'azar}
\affil{\cca}

\author{Megan Bedell}
\affil{\cca}

@@

\begin{figure*}
\plotone{fig/cartoon.pdf}
\caption{Caption.}
\label{fig:cartoon}
\end{figure*}

@@

We use the code \texttt{gala} v0.3 to perform orbit integrations and
conversion to action space \citep{2017JOSS....2..388P,Price-Whelan:2018},
which uses an action estimator technique presented by
\citet{2014MNRAS.441.3284S}. We use the default \texttt{MWPotential} as our
potential, which is based on the Milky Way potential available in
\texttt{galpy} \citep{2015ApJS..216...29B}. This potential includes a
Hernquist bulge and nucleus \citep{1990ApJ...356..359H}, a Miyamoto-Nagai disk
\citep{1975PASJ...27..533M}, and an NFW halo \citep{1997ApJ...490..493N}, and
is fit to empirically match some observations. We use the Dormand-Prince
8(5,3) integration scheme \citep{Dormand80:integrator}. We use a timestep of
$1\,\Myr$ and integrate for $5\,\Gyr$, corresponding to $\sim 20$ orbits for
a Sun-like star.

First, we illustrate the time-dependence of one possible inaccurate reference
frame. We begin by taking an orbit with initial position $(8, 0, 0)\,\kpc$ and
initial velocity $(0, -190, 50)\,\kms$ --- this corresponds to an orbit with
actions $(J_r, L_z, J_z) = (32.5, -1520, 23.0)\,\actunit$. The orbit is
plotted in \Gus{Appendix x}. We then suppose that an observer makes
observations of this orbit in a reference frame that is incorrect in radius by
$200\,\pc$ and height by $100\,\pc$ --- we subtract the vector $(200, 0,
100)\,\pc$ from each position in the orbit. This corresponds to an observer
physically located at the position $(8, 0, 0)\,\kpc$ but erroneously thinking
they are located at $(8.2, 0, 0.1)\,\kpc$.

Using the observations of the orbit that this erroneous observer makes every
$\Myr$, we perform the same orbit integration procedure as before to compute
the actions our observer would make in the incorrect reference frame over the
duration of the orbit. The erroneous computed actions are shown for the first
$\Gyr$ of the orbit in Figure~\ref{fig:one_orbit_wrong_ref}. Occasionally the
numerical scheme fails and very large actions are reported by \texttt{gala}
--- we perform a $5\sigma$ clip on each action to exclude such orbits, but
this only excludes a total of $5$ orbits out of the $1000$ considered for
Figure~\ref{fig:one_orbit_wrong_ref}. Some numerical artifacts remain, but the
vast majority of orbits are computed properly.

\begin{figure*}
\plotone{fig/one_orbit.pdf}
\caption{Caption.}
\label{fig:one_orbit_wrong_ref}
\end{figure*}

@@

To compute the forces from the frozen potential, we use the simple tree code
\texttt{pykdgrav}\footnote{\url{https://github.com/omgspace/pykdgrav},
commit:\texttt{fbd1ddc}}. We use an opening angle of $0.5$ and exclude stars
at distances $R>50\,\kpc$ in the fiducial reference frame.

We use the initial position and velocity of two star particles in
$\texttt{m12i}$. These two star particles are randomly chosen from all star
particles in the simulation with the following properties:
